Glossary

### 2025-05-02 glossary.qmd
further small edits

@@

[Perperoglou 2019](https://doi.org/10.1186/s12874-019-0666-3)

@@

The functional form of continuous covariates in statistics refers to the mathematical relationship between the independent variable and the dependent variable. This can be linear, nonlinear, or a combination of both. The choice of functional form can have a significant impact on the results of statistical analysis and should be carefully considered when selecting a model.
### Spline function

A spline function is a type of mathematical function used in statistics and numerical analysis to approximate complex curves or surfaces. It consists of multiple polynomial segments that join smoothly at specific points called knots. Spline functions are flexible and can be used to fit data or smooth curves.
### R (software)

@@

@@

[Bach 2020](https://doi.org/10.1371/journal.pone.0241427)

@@

@@

[Sauerbrei 2020](https://doi.org/10.1186/s41512-020-00074-3)

@@

@@

[Wallisch 2022](https://doi.org/10.1371/journal.pone.0262918)

@@

[Ullmann 2024](https://doi.org/10.1371/journal.pone.0308543)

@@

@@

[Heinze 2024](https://doi.org/10.1186/s12874-024-02294-3)

>>>>

On this page, you find descriptions of all keywords used in our papers.

## Keywords used in [Perperoglou 2019](https://doi.org/10.1186/s12874-019-0666-3)

@@

@@

The functional form of continuous covariates in statistics refers to the mathematical relationship between the independent variable and the dependent variable. This can be linear, nonlinear, or a combination of both. The choice of functional form can have a significant impact on the results of statistical analysis and should be carefully considered when selecting a model.

### Spline function

A spline function is a type of mathematical function used in statistics and numerical analysis to approximate complex curves or surfaces. It consists of multiple polynomial segments that join smoothly at specific points called knots. Spline functions are flexible and can be used to fit data or smooth curves.

### R (software)

@@

## Keywords used in [Bach 2020](https://doi.org/10.1371/journal.pone.0241427)

@@

@@

## Keywords used in [Sauerbrei 2020](https://doi.org/10.1186/s41512-020-00074-3)

@@

@@

## Keywords used in [Wallisch 2022](https://doi.org/10.1371/journal.pone.0262918)

@@

## Keywords used in [Ullmann 2024](https://doi.org/10.1371/journal.pone.0308543)

@@

@@

## Keywords used in [Heinze 2024](https://doi.org/10.1186/s12874-024-02294-3)

@@
